Stimming paper

### 2023-09-06 manuscript.qmd
First version of analysis pipeline

processdata <- 1

# install R packages
packagelist <- c('knitr','reticulate','osfr','bookdown') 
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

if (!dir.exists('local/processed')){dir.create('local/processed')}

@@

if r.processdata==1:

@@

  ANT_montage = mne.channels.make_standard_montage("standard_1020")
  reject_criteria = dict(eeg=150e-6)

  for subj in range(501,503):
    filename = "local/preprocessed/S" + str(subj) + ".set"
    raw = mne.io.read_raw_eeglab(filename,preload=True)
    raw.drop_channels(["HEOG", "VEOG"])
    raw.set_montage(ANT_montage)

@@

    events, _ = mne.events_from_annotations(filtered)

    event_dict = {
        "cueleft": 4,
        "cueright": 5,
    }

@@

    cueepochs = epochs["cueleft", "cueright"]
    X = cueepochs.get_data()  # MEG signals: n_epochs, n_meg_channels, n_times
    y = cueepochs.events[:, 2]  # target: auditory left vs visual left

    clf = make_pipeline(StandardScaler(), LogisticRegression(solver="liblinear"))

    time_decod = SlidingEstimator(clf, n_jobs=None, scoring="roc_auc", verbose=True)

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=None)

    # Mean scores across cross-validation splits
    scores = np.mean(scores, axis=0)

    filename = "local/processed/S" + str(subj) + "_decoding.csv"

    times = pd.Series(range(-200,1001))
    scores = pd.Series(scores)

    output = pd.concat([times,scores],axis=1)
    output.columns = ['Time','Accuracy']

@@

>>>>

processdata <- 0

# install R packages
packagelist <- c('knitr','reticulate','osfr','bookdown','grImport','tiff','rstatix','ez') 
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

if (!dir.exists('local/processedE1')){dir.create('local/processedE1')}
if (!dir.exists('local/processedE2')){dir.create('local/processedE2')}

getcleanmean <- function(input){
  s <- dim(input)
  allsds <- apply(input,c(1,3),sd)
  thresh <- quantile(allsds,0.95)
  allmeans <- matrix(0,nrow=s[2],ncol=s[3])
  for (ch in 1:s[3]){
    temp <- allsds[,ch]
    i <- which(temp<thresh)
    allmeans[,ch] <- colMeans(input[i,,ch])
  }
return(allmeans)}

getcleanCI <- function(input){
  s <- dim(input)
  allsds <- apply(input,c(1,3),sd)
  thresh <- quantile(allsds,0.95)
  allCI <- matrix(0,nrow=s[2],ncol=s[3])
  for (ch in 1:s[3]){
    temp <- allsds[,ch]
    i <- which(temp<thresh)
    allCI[,ch] <- 1.96*apply(input[i,,ch],2,sd)/sqrt(length(i))
  }
return(allCI)}

flatalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1]*alpha + 1-alpha, x[2]*alpha + 1-alpha, x[3]*alpha + 1-alpha))}

v4Interp <- function(df, xo, yo, rmax = .75, gridRes = 67) {
  ## Create a function to perform Matlab's v4 interpolation.
  ## Takes as input a data-frame with columns x, y, and z (x co-ordinates, y co-ordinates, and amplitude)
  ## and variables xo and yo, the co-ordinates which will be use to create a grid for interpolation
  xo <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
  yo <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
  xy <- df$x + df$y*sqrt(as.complex(-1))
  d <- matrix(rep(xy,length(xy)),nrow = length(xy), ncol = length(xy))
  d <- abs(d - t(d))
  diag(d) <- 1
  g <- (d^2) * (log(d)-1)   # Green's function.
  diag(g) <- 0
  weights <- qr.solve(g,df$z)
  xy <- t(xy)
  outmat <- matrix(nrow = gridRes,ncol = gridRes)
  for (i in 1:gridRes){
    for (j in 1:gridRes) {
      test4 <- abs((xo[i,j] + sqrt(as.complex(-1))*yo[i,j]) - xy)
      g <- (test4^2) * (log(test4)-1)
      outmat[i,j] <- g %*% weights}}
  outDf <- data.frame(x = xo[,1],outmat)
  names(outDf)[1:length(yo[1,])+1] <- yo[1,]
  return(outDf)}

mnechans <- read.csv('local/MNEchannels.csv')
mnechans <- mnechans[c(1:12,14:18,20:64),1]  # exclude the mastoids

chandata <- read.csv('local/channeldata.csv')

electrodeindices <- match(toupper(mnechans),chandata$Electrode)

figdir <- 'Figures/'

@@

if r.processdata==2:

@@

  ANT_montage = mne.channels.make_standard_montage("standard_1020")
  reject_criteria = None   #dict(eeg=150e-6)

  clf = make_pipeline(StandardScaler(), LogisticRegression(solver="liblinear"))
  time_decod = SlidingEstimator(clf, n_jobs=10, scoring="roc_auc", verbose=True)

  legaltriggers = {
    "1": 1,
    "11": 2,
    "12": 3,
    "201": 4,
    "202": 5,
    "21": 6,
    "22": 7,
    "31": 8,
    "32": 9   
    }
  sublist = list(range(501,506)) + list(range(508,542))

  for subj in range(0,len(sublist)):
    filename = "local/preprocessed/S" + str(sublist[subj]) + ".set"
    raw = mne.io.read_raw_eeglab(filename,preload=True)
    raw.drop_channels(["HEOG", "VEOG", "M1", "M2"])
    raw.set_montage(ANT_montage)

@@

    events, _ = mne.events_from_annotations(filtered, event_id=legaltriggers)

    event_dict = {
        "cueleft": 4,
        "cueright": 5,
        "targetleft/top": 2,
        "targetleft/bottom": 3,
        "targetright/top": 6,
        "targetright/bottom": 7,
        "responsetop": 8,
        "responsebottom": 9
    }

@@

    epochs.equalize_event_counts(["cueleft", "cueright"])
    cueepochs = epochs["cueleft", "cueright"]
    X = cueepochs.get_data()  # EEG signals: n_epochs, n_meg_channels, n_times
    y = cueepochs.events[:, 2]  # target: auditory left vs visual left

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    cuedecode = np.mean(scores, axis=0)

    epochs.equalize_event_counts(["targetleft", "targetright"])
    targetepochs = epochs["targetleft", "targetright"]
    X = targetepochs.get_data()  
    y = targetepochs.events[:, 2]  # target: auditory left vs visual left
    y[y<5] = 1     # relabel the left and right conditions as 1 and 2
    y[y>5] = 2
    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    targetu = np.mean(scores, axis=0)

    newevents, _ = mne.events_from_annotations(filtered, event_id=legaltriggers)

    for i in range(1,len(events)):
        if events[i,2]==4:
            if events[i+1,2]==2:
                newevents[i+1,2] = 11    #congruent left
            if events[i+1,2]==3:
                newevents[i+1,2] = 11    #congruent left
            if events[i+1,2]==6:
                newevents[i+1,2] = 14    #incongruent right   
            if events[i+1,2]==7:
                newevents[i+1,2] = 14    #incongruent right
        if events[i,2]==5:
             if events[i+1,2]==2:
                 newevents[i+1,2] = 13    #incongruent left
             if events[i+1,2]==3:
                 newevents[i+1,2] = 13    #incongruent left
             if events[i+1,2]==6:
                 newevents[i+1,2] = 12    #congruent right
             if events[i+1,2]==7:
                 newevents[i+1,2] = 12    #congruent right

    event_dict2 = {
         "congruent/left": 11,
         "congruent/right": 12,
         "incongruent/left": 13,
         "incongruent/right": 14     
     }

    epochsCI = mne.Epochs(
        filtered,
        newevents,
        event_id=event_dict2,
        tmin=-0.2,
        tmax=1,
        reject=reject_criteria,
        preload=True,
    )

    epochsCI.equalize_event_counts(["congruent", "incongruent"])
    targetepochs = epochsCI["congruent", "incongruent"]
    X = targetepochs.get_data()  
    y = targetepochs.events[:, 2]  # target: auditory left vs visual left
    y[y<13] = 1     # relabel the left and right conditions as 1 and 2
    y[y>12] = 2

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    congincong = np.mean(scores, axis=0)

    epochsCI.equalize_event_counts(["left", "right"])
    targetepochs = epochsCI["left", "right"]
    X = targetepochs.get_data() 
    y = targetepochs.events[:, 2]  # target: auditory left vs visual left
    y[y==13] = 1     # relabel the left and right conditions as 1 and 2
    y[y==14] = 2

    i1 = np.array(np.where(y==11))
    i2 = np.random.permutation(i1.shape[1])
    y[i1[0,i2[0:49]]] = 1
    i1 = np.array(np.where(y==12))
    i2 = np.random.permutation(i1.shape[1])
    y[i1[0,i2[0:49]]] = 2
    i1 = np.array(np.where(y<10))
    y = y[i1[0,:]]
    X = X[i1[0,:],:,:]

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    targetb = np.mean(scores, axis=0)

    # export decoding results to csv text files
    filename = "local/processedE1/S" + str(sublist[subj]) + "_decoding.csv"

    times = pd.Series(range(-200,1001))
    cuedecode = pd.Series(cuedecode)
    targetu = pd.Series(targetu)
    congincong = pd.Series(congincong)
    targetb = pd.Series(targetb)

    output = pd.concat([times,cuedecode,targetu,congincong,targetb],axis=1)
    output.columns = ['Time','Cue','TargetU','CongIncong','TargetB']

@@

    filename = "local/processedE1/S" + str(sublist[subj]) + "_cueleft.csv"
    ERP = epochs["cueleft"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE1/S" + str(sublist[subj]) + "_cueright.csv"
    ERP = epochs["cueright"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE1/S" + str(sublist[subj]) + "_targetleft.csv"
    ERP = epochs["targetleft"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE1/S" + str(sublist[subj]) + "_targetright.csv"
    ERP = epochs["targetright"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE1/S" + str(sublist[subj]) + "_events.csv"
    dataout = np.asarray(events)
    np.savetxt(filename, dataout, delimiter=",")

```{python ProcessExpt2}

if r.processdata==2:

  ANT_montage = mne.channels.make_standard_montage("standard_1020")
  reject_criteria = None   #dict(eeg=150e-6)

  clf = make_pipeline(StandardScaler(), LogisticRegression(solver="liblinear"))
  time_decod = SlidingEstimator(clf, n_jobs=10, scoring="roc_auc", verbose=True)

  legaltriggers = {
    "1": 1,
    "11": 2,
    "12": 3,
    "101": 4,
    "102": 5,
    "21": 6,
    "22": 7,
    "31": 8,
    "32": 9,
    "2": 10
    }
  sublist = list(range(201,202)) + list(range(204,213)) + list(range(214,226))

  for subj in range(0,len(sublist)):
    filename = "local/preprocessed/S" + str(sublist[subj]) + ".set"

    raw = mne.io.read_raw_eeglab(filename,preload=True)
    raw.drop_channels(["HEOG", "VEOG", "M1", "M2"])
    raw.set_montage(ANT_montage)

    events, _ = mne.events_from_annotations(filtered, event_id=legaltriggers)

    event_dict = {
        "cueleft": 4,
        "cueright": 5,
        "targetleft/top": 2,
        "targetleft/bottom": 3,
        "targetright/top": 6,
        "targetright/bottom": 7,
        "responsetop": 8,
        "responsebottom": 9,
        "nonstimming": 1,
        "stimming": 10
    }

    epochs.equalize_event_counts(["cueleft", "cueright"])
    cueepochs = epochs["cueleft", "cueright"]
    X = cueepochs.get_data()  # EEG signals: n_epochs, n_meg_channels, n_times
    y = cueepochs.events[:, 2]  # target: auditory left vs visual left

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    cuedecode = np.mean(scores, axis=0)

    epochs.equalize_event_counts(["targetleft", "targetright"])
    targetepochs = epochs["targetleft", "targetright"]
    X = targetepochs.get_data()  
    y = targetepochs.events[:, 2]  # target: auditory left vs visual left
    y[y<5] = 1     # relabel the left and right conditions as 1 and 2
    y[y>5] = 2
    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    targetu = np.mean(scores, axis=0)

    newevents, _ = mne.events_from_annotations(filtered, event_id=legaltriggers)

    for i in range(1,len(events)):
        if events[i,2]==4:
            if events[i+1,2]==2:
                newevents[i+1,2] = 11    #congruent left
            if events[i+1,2]==3:
                newevents[i+1,2] = 11    #congruent left
            if events[i+1,2]==6:
                newevents[i+1,2] = 14    #incongruent right   
            if events[i+1,2]==7:
                newevents[i+1,2] = 14    #incongruent right
        if events[i,2]==5:
             if events[i+1,2]==2:
                 newevents[i+1,2] = 13    #incongruent left
             if events[i+1,2]==3:
                 newevents[i+1,2] = 13    #incongruent left
             if events[i+1,2]==6:
                 newevents[i+1,2] = 12    #congruent right
             if events[i+1,2]==7:
                 newevents[i+1,2] = 12    #congruent right

    event_dict2 = {
         "congruent/left": 11,
         "congruent/right": 12,
         "incongruent/left": 13,
         "incongruent/right": 14     
     }

    epochsCI = mne.Epochs(
        filtered,
        newevents,
        event_id=event_dict2,
        tmin=-0.2,
        tmax=1,
        reject=reject_criteria,
        preload=True,
    )

    epochsCI.equalize_event_counts(["congruent", "incongruent"])
    targetepochs = epochsCI["congruent", "incongruent"]
    X = targetepochs.get_data()  
    y = targetepochs.events[:, 2]  # target: auditory left vs visual left
    y[y<13] = 1     # relabel the left and right conditions as 1 and 2
    y[y>12] = 2

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    congincong = np.mean(scores, axis=0)

    epochsCI.equalize_event_counts(["left", "right"])
    targetepochs = epochsCI["left", "right"]
    X = targetepochs.get_data() 
    y = targetepochs.events[:, 2]  # target: auditory left vs visual left
    y[y==13] = 1     # relabel the left and right conditions as 1 and 2
    y[y==14] = 2

    i1 = np.array(np.where(y==11))
    i2 = np.random.permutation(i1.shape[1])
    y[i1[0,i2[0:49]]] = 1
    i1 = np.array(np.where(y==12))
    i2 = np.random.permutation(i1.shape[1])
    y[i1[0,i2[0:49]]] = 2
    i1 = np.array(np.where(y<10))
    y = y[i1[0,:]]
    X = X[i1[0,:],:,:]

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    targetb = np.mean(scores, axis=0)

    filename = "local/processedE2/S" + str(sublist[subj]) + "_cueleft.csv"
    ERP = epochs["cueleft"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE2/S" + str(sublist[subj]) + "_cueright.csv"
    ERP = epochs["cueright"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE2/S" + str(sublist[subj]) + "_targetleft.csv"
    ERP = epochs["targetleft"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE2/S" + str(sublist[subj]) + "_targetright.csv"
    ERP = epochs["targetright"].average()
    dataout = np.transpose(np.asarray(ERP.data))*1000000
    np.savetxt(filename, dataout, delimiter=",")

    filename = "local/processedE2/S" + str(sublist[subj]) + "_events.csv"
    dataout = np.asarray(events)
    np.savetxt(filename, dataout, delimiter=",")

    newevents2, _ = mne.events_from_annotations(filtered, event_id=legaltriggers)
    stimcond = 0

    for i in range(0,len(events)):
        if events[i,2] == 1: stimcond = 1 
        if events[i,2] == 10: stimcond = 2 
        if events[i,2] in range(2,10): newevents2[i,2] = events[i,2] + (100*stimcond)

    event_dict3 = {
        "nostimcueleft": 104,
        "nostimcueright": 105,
        "nostimtargetleft/top": 102,
        "nostimtargetleft/bottom": 103,
        "nostimtargetright/top": 106,
        "nostimtargetright/bottom": 107,
        "stimcueleft": 204,
        "stimcueright": 205,
        "stimtargetleft/top": 202,
        "stimtargetleft/bottom": 203,
        "stimtargetright/top": 206,
        "stimtargetright/bottom": 207
    }

    splitepochs = mne.Epochs(
        filtered,
        newevents2,
        event_id=event_dict3,
        tmin=-0.2,
        tmax=1,
        reject=reject_criteria,
        preload=True,
    )

    splitepochs.equalize_event_counts(["nostimcueleft", "nostimcueright"])
    cueepochs2 = splitepochs["nostimcueleft", "nostimcueright"]
    X = cueepochs2.get_data()  # EEG signals: n_epochs, n_meg_channels, n_times
    y = cueepochs2.events[:, 2]-100  # target: auditory left vs visual left

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    cuedecodeNostim = np.mean(scores, axis=0)

    splitepochs.equalize_event_counts(["nostimtargetleft", "nostimtargetright"])
    targetepochs2 = splitepochs["nostimtargetleft", "nostimtargetright"]
    X = targetepochs2.get_data()
    y = targetepochs2.events[:, 2]  # target: auditory left vs visual left
    y[y<105] = 1     # relabel the left and right conditions as 1 and 2
    y[y>105] = 2
    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    targetuNostim = np.mean(scores, axis=0)

    splitepochs.equalize_event_counts(["stimcueleft", "stimcueright"])
    cueepochs3 = splitepochs["stimcueleft", "stimcueright"]
    X = cueepochs3.get_data()  # EEG signals: n_epochs, n_meg_channels, n_times
    y = cueepochs3.events[:, 2]-200  # target: auditory left vs visual left

    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    cuedecodeStim = np.mean(scores, axis=0)

    splitepochs.equalize_event_counts(["stimtargetleft", "stimtargetright"])
    targetepochs3 = splitepochs["stimtargetleft", "stimtargetright"]
    X = targetepochs3.get_data()
    y = targetepochs3.events[:, 2]  # target: auditory left vs visual left
    y[y<205] = 1     # relabel the left and right conditions as 1 and 2
    y[y>205] = 2
    scores = cross_val_multiscore(time_decod, X, y, cv=10, n_jobs=10)
    targetuStim = np.mean(scores, axis=0)

    # export decoding results to csv text files
    filename = "local/processedE2/S" + str(sublist[subj]) + "_decoding.csv"

    times = pd.Series(range(-200,1001))
    cuedecode = pd.Series(cuedecode)
    targetu = pd.Series(targetu)
    congincong = pd.Series(congincong)
    targetb = pd.Series(targetb)
    cuedecodeN = pd.Series(cuedecodeNostim)
    cuedecodeS = pd.Series(cuedecodeStim)
    targetuN = pd.Series(targetuNostim)
    targetuS = pd.Series(targetuStim)

    output = pd.concat([times,cuedecode,targetu,congincong,targetb,cuedecodeN,cuedecodeS,targetuN,targetuS],axis=1)
    output.columns = ['Time','Cue','TargetU','CongIncong','TargetB','CueNostim','CueStim','TargetUNostim','TargetUStim']

```{r collateprocessed1}
#| warning: false

if (processdata>0){

  d <- dir('local/processedE1',pattern='*_decoding.csv',full.names=TRUE)

  allCue <- matrix(0,nrow=1201,ncol=length(d))
  allTargetU <- matrix(0,nrow=1201,ncol=length(d))
  allCongIncong <- matrix(0,nrow=1201,ncol=length(d))
  allTargetB <- matrix(0,nrow=1201,ncol=length(d))
  for (s in 1:length(d)){
    decodingdata <- read.csv(d[s])
    allCue[,s] <- decodingdata$Cue
    allTargetU[,s] <- decodingdata$TargetU
    allCongIncong[,s] <- decodingdata$CongIncong
    allTargetB[,s] <- decodingdata$TargetB
  }

  meandecoding <- decodingdata
  meandecoding$Cue <- rowMeans(allCue)
  meandecoding$TargetU <- rowMeans(allTargetU)
  meandecoding$CongIncong <- rowMeans(allCongIncong)
  meandecoding$TargetB <- rowMeans(allTargetB)

  CIdecoding <- decodingdata
  CIdecoding$Cue <- apply(allCue,1,sd)/sqrt(ncol(allCue))*1.96
  CIdecoding$TargetU <- apply(allTargetU,1,sd)/sqrt(ncol(allTargetU))*1.96
  CIdecoding$CongIncong <- apply(allCongIncong,1,sd)/sqrt(ncol(allCongIncong))*1.96
  CIdecoding$TargetB <- apply(allTargetB,1,sd)/sqrt(ncol(allTargetB))*1.96

  d <- dir('local/processedE1',pattern='*_cueleft.csv',full.names=TRUE)
  allcueleft <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    allcueleft[s,,] <- as.matrix(ERPdata)
  }
  d <- dir('local/processedE1',pattern='*_cueright.csv',full.names=TRUE)
  allcueright <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    allcueright[s,,] <- as.matrix(ERPdata)
  }
  d <- dir('local/processedE1',pattern='*_targetleft.csv',full.names=TRUE)
  alltargetleft <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    alltargetleft[s,,] <- as.matrix(ERPdata)
  }
  d <- dir('local/processedE1',pattern='*_targetright.csv',full.names=TRUE)
  alltargetright <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    alltargetright[s,,] <- as.matrix(ERPdata)
  }

  meancueleft <- getcleanmean(allcueleft)
  meancueright <- getcleanmean(allcueright)
  meantargetleft <- getcleanmean(alltargetleft)
  meantargetright <- getcleanmean(alltargetright)

  CIcueleft <- getcleanCI(allcueleft)
  CIcueright <- getcleanCI(allcueright)
  CItargetleft <- getcleanCI(alltargetleft)
  CItargetright <- getcleanCI(alltargetright)

  save(file='local/Exp1Group.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright'))

}

```{r collateprocessed2}
#| warning: false

if (processdata>0){

  d <- dir('local/processedE2',pattern='*_decoding.csv',full.names=TRUE)

  allCue <- matrix(0,nrow=1201,ncol=length(d))
  allTargetU <- matrix(0,nrow=1201,ncol=length(d))
  allCongIncong <- matrix(0,nrow=1201,ncol=length(d))
  allTargetB <- matrix(0,nrow=1201,ncol=length(d))
  allCueNostim <- matrix(0,nrow=1201,ncol=length(d))
  allCueStim <- matrix(0,nrow=1201,ncol=length(d))
  for (s in 1:length(d)){
    decodingdata <- read.csv(d[s])
    allCue[,s] <- decodingdata$Cue
    allTargetU[,s] <- decodingdata$TargetU
    allCongIncong[,s] <- decodingdata$CongIncong
    allTargetB[,s] <- decodingdata$TargetB
    allCueNostim[,s] <- decodingdata$CueNostim
    allCueStim[,s] <- decodingdata$CueStim
  }

  meandecoding <- decodingdata
  meandecoding$Cue <- rowMeans(allCue)
  meandecoding$TargetU <- rowMeans(allTargetU)
  meandecoding$CongIncong <- rowMeans(allCongIncong)
  meandecoding$TargetB <- rowMeans(allTargetB)
  meandecoding$CueNostim <- rowMeans(allCueNostim)
  meandecoding$CueStim <- rowMeans(allCueStim)

  CIdecoding <- decodingdata
  CIdecoding$Cue <- apply(allCue,1,sd)/sqrt(ncol(allCue))*1.96
  CIdecoding$TargetU <- apply(allTargetU,1,sd)/sqrt(ncol(allTargetU))*1.96
  CIdecoding$CongIncong <- apply(allCongIncong,1,sd)/sqrt(ncol(allCongIncong))*1.96
  CIdecoding$TargetB <- apply(allTargetB,1,sd)/sqrt(ncol(allTargetB))*1.96
  CIdecoding$CueNoStim <- apply(allCueNoStim,1,sd)/sqrt(ncol(allCueNoStim))*1.96
  CIdecoding$CueStim <- apply(allCueStim,1,sd)/sqrt(ncol(allCueStim))*1.96

  d <- dir('local/processedE2',pattern='*_cueleft.csv',full.names=TRUE)
  allcueleft <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    allcueleft[s,,] <- as.matrix(ERPdata)
  }
  d <- dir('local/processedE2',pattern='*_cueright.csv',full.names=TRUE)
  allcueright <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    allcueright[s,,] <- as.matrix(ERPdata)
  }
  d <- dir('local/processedE2',pattern='*_targetleft.csv',full.names=TRUE)
  alltargetleft <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    alltargetleft[s,,] <- as.matrix(ERPdata)
  }
  d <- dir('local/processedE2',pattern='*_targetright.csv',full.names=TRUE)
  alltargetright <- array(0,dim=c(length(d),1201,62))
  for (s in 1:length(d)){
    ERPdata <- read.csv(d[s],header=FALSE)
    alltargetright[s,,] <- as.matrix(ERPdata)
  }

  meancueleft <- getcleanmean(allcueleft)
  meancueright <- getcleanmean(allcueright)
  meantargetleft <- getcleanmean(alltargetleft)
  meantargetright <- getcleanmean(alltargetright)

  CIcueleft <- getcleanCI(allcueleft)
  CIcueright <- getcleanCI(allcueright)
  CItargetleft <- getcleanCI(alltargetleft)
  CItargetright <- getcleanCI(alltargetright)

  save(file='local/Exp2Group.RData',list=c('meandecoding','CIdecoding','meancueleft','CIcueleft','meancueright','CIcueright','meantargetleft','CItargetleft','meantargetright','CItargetright'))

}

```{r analyseresponses1}
#| warning: false

if (processdata>0){

  d <- dir('local/processedE1',pattern='_events.csv',full.names=TRUE)

  allRT <- matrix(0, nrow=length(d), 2)
  allaccuracy <- matrix(0, nrow=length(d), 2)

  for (s in 1:length(d)){
  respdata <- read.csv(d[s],header=FALSE)

  cueside <- NULL
  targetside <- NULL
  targetpos <- NULL
  iscorrect <- NULL
  RT <- NULL
  trialcount <- 0
  listpos <- 0

  while (listpos<nrow(respdata)){
    listpos <- listpos + 1
    if (sum(respdata[listpos,3]==c(4,5))){
      trialcount <- trialcount + 1
      cueside[trialcount] <- respdata[listpos,3]-3
    }
    if (sum(respdata[listpos,3]==c(2,3,6,7))){
      targetonset <- respdata[listpos,1]
    }        
    if (sum(respdata[listpos,3]==c(2,3))){
      targetside[trialcount] <- 1
    }    
    if (sum(respdata[listpos,3]==c(6,7))){
      targetside[trialcount] <- 2
    }   
    if (sum(respdata[listpos,3]==c(2,6))){
      targetpos[trialcount] <- 1
    }    
    if (sum(respdata[listpos,3]==c(3,7))){
      targetpos[trialcount] <- 2
    }

    if (sum(respdata[listpos,3]==c(8,9))){
      if ((respdata[listpos,3]==8) & (targetpos[trialcount]==1)){iscorrect[trialcount] <- 0}
      if ((respdata[listpos,3]==8) & (targetpos[trialcount]==2)){iscorrect[trialcount] <- 1}
      if ((respdata[listpos,3]==9) & (targetpos[trialcount]==1)){iscorrect[trialcount] <- 1}
      if ((respdata[listpos,3]==9) & (targetpos[trialcount]==2)){iscorrect[trialcount] <- 0}
      RT[trialcount] <- respdata[listpos,1] - targetonset
    }

  }

  congincong <- cueside==targetside
  subjresps <- data.frame(cueside,targetside,congincong,targetpos,iscorrect,RT)

  allcong <- subset(subjresps,congincong==TRUE)
  allaccuracy[s,1] <- mean(allcong$iscorrect)
  allRT[s,1] <- mean(20*log10(allcong$RT))
  allincong <- subset(subjresps,congincong==FALSE)
  allaccuracy[s,2] <- mean(allincong$iscorrect)
  allRT[s,2] <- mean(20*log10(allincong$RT))
  }

  save(file='local/Expt1resps.RData',list=c('allRT','allaccuracy'))
}

load('local/Expt1resps.RData')

ACCtest <- t.test(allaccuracy[,1],allaccuracy[,2],paired=TRUE)
temp <- allaccuracy[,1]-allaccuracy[,2]
ACCd <- abs(mean(temp))/sd(temp)
accdiff <- 100*(mean(allaccuracy[,1])-mean(allaccuracy[,2]))

RTtest <- t.test(allRT[,1],allRT[,2],paired=TRUE)
temp <- allRT[,1]-allRT[,2]
RTd <- abs(mean(temp))/sd(temp)
RTdiff <- 10^(mean(allRT[,2])/20)-10^(mean(allRT[,1])/20)

```{r analyseresponses2}
#| warning: false

if (processdata>0){

  d <- dir('local/processedE2',pattern='_events.csv',full.names=TRUE)

  allRT <- matrix(0, nrow=length(d), 4)
  allaccuracy <- matrix(0, nrow=length(d), 4)

  for (s in 1:length(d)){
  respdata <- read.csv(d[s],header=FALSE)

  cueside <- NULL
  targetside <- NULL
  targetpos <- NULL
  iscorrect <- NULL
  RT <- NULL
  stimcond <- NULL
  trialcount <- 0
  listpos <- 0
  stimblock <- 0

  while (listpos<nrow(respdata)){
    listpos <- listpos + 1
    if (respdata[listpos,3]==1){stimblock <- 1}
    if (respdata[listpos,3]==10){stimblock <- 2}

    if (sum(respdata[listpos,3]==c(4,5))){
      trialcount <- trialcount + 1
      cueside[trialcount] <- respdata[listpos,3]-3
    }
    if (sum(respdata[listpos,3]==c(2,3,6,7))){
      targetonset <- respdata[listpos,1]
    }        
    if (sum(respdata[listpos,3]==c(2,3))){
      targetside[trialcount] <- 1
    }    
    if (sum(respdata[listpos,3]==c(6,7))){
      targetside[trialcount] <- 2
    }   
    if (sum(respdata[listpos,3]==c(2,6))){
      targetpos[trialcount] <- 1
    }    
    if (sum(respdata[listpos,3]==c(3,7))){
      targetpos[trialcount] <- 2
    }

    stimcond[trialcount] <- stimblock

    if (sum(respdata[listpos,3]==c(8,9))){
      if ((respdata[listpos,3]==8) & (targetpos[trialcount]==1)){iscorrect[trialcount] <- 0}
      if ((respdata[listpos,3]==8) & (targetpos[trialcount]==2)){iscorrect[trialcount] <- 1}
      if ((respdata[listpos,3]==9) & (targetpos[trialcount]==1)){iscorrect[trialcount] <- 1}
      if ((respdata[listpos,3]==9) & (targetpos[trialcount]==2)){iscorrect[trialcount] <- 0}
      RT[trialcount] <- respdata[listpos,1] - targetonset
    }

  }

  congincong <- cueside==targetside
  subjresps <- data.frame(stimcond,cueside,targetside,congincong,targetpos,iscorrect,RT)

  temp <- subset(subjresps,stimcond==1)
  allcong <- subset(temp,congincong==TRUE)
  allaccuracy[s,1] <- mean(allcong$iscorrect)
  allRT[s,1] <- mean(20*log10(allcong$RT))
  allincong <- subset(temp,congincong==FALSE)
  allaccuracy[s,2] <- mean(allincong$iscorrect)
  allRT[s,2] <- mean(20*log10(allincong$RT))

  temp <- subset(subjresps,stimcond==2)
  allcong <- subset(temp,congincong==TRUE)
  allaccuracy[s,3] <- mean(allcong$iscorrect)
  allRT[s,3] <- mean(20*log10(allcong$RT))
  allincong <- subset(temp,congincong==FALSE)
  allaccuracy[s,4] <- mean(allincong$iscorrect)
  allRT[s,4] <- mean(20*log10(allincong$RT))

  }

  save(file='local/Expt2resps.RData',list=c('allRT','allaccuracy'))
}

load('local/Expt2resps.RData')

# restructure for 2x2 ANOVA

accuracy <- as.vector(allaccuracy)
participant <- as.factor(rep(1:nrow(allaccuracy),4))
stimcond <- as.factor(rep(1:2,each=(2*nrow(allaccuracy))))
congruent <- as.factor(rep(1:2,each=nrow(allaccuracy),2))
accuracyaov <- data.frame(accuracy,participant,stimcond,congruent)
accAOVresults <- ezANOVA(accuracyaov, dv=accuracy, wid=participant, within=c(stimcond,congruent))
